formula1

### 2020-05-29 inst/formula1.Rmd
now called keep_flawed()
get rid of that stupid 'misslast' argument

```{r cars}
f2017 <- read.table("formula1_2017.txt",header=TRUE)
head(f2017)
```

@@

```{r,likelihoodandscore}
points <- f2017$points
names(points) <- f2017$driver

@@

```{r,testwetstrengthzero}
pnames(H)
H9 <- keep(H,c("S",pnames(H)[1:8]))
specificp.gt.test(H9,"S",0)
```

>>>>

```{r cars}
f2017 <- read.table("formula1_2017.txt",header=TRUE)
f2017 <- f2017[,1:20]  # final column is points
head(f2017)
```

@@

```{r,likelihoodandscore}
jj <- read.table("formula1_2017.txt",header=TRUE)
points <- jj[,21]
names(points) <- rownames(jj)

@@

```{r,testwetstrengthzero}
pnames(H)
H9 <- keep_flawed(H,c("S",pnames(H)[1:8]))
specificp.gt.test(H9,"S",0)
```
